Matching Bullets

### 2015-12-10 imaging-paper.Rnw
More smoothing factor work...

\subsection{Varying smoothing factor}
As mentioned, the algorithm for peak/valley detection depends on the selection of a smoothing window, called the smoothing factor. In particular, for detecting and removing the grooves prior to fitting a Loess regression, we selected a smoothing factor of 35

>>>>

\subsection{Varying smoothing factor}
As mentioned, the algorithm for peak/valley detection depends on the selection of a smoothing window, called the smoothing factor. In particular, for detecting and removing the grooves prior to fitting a Loess regression, we selected a smoothing factor of 35. We can investigate the performance of groove detection across different smoothing factors.

\begin{figure}[hbtp]
\centering
\begin{subfigure}[t]{\linewidth}
\caption{Crosscuts at $x = 100$.\label{fig:smoothfac1}}{%
<<smoothfac1, echo=FALSE, fig.width=7, fig.height=2, out.width='\\textwidth'>>=
get_grooves(br111_bullet, smoothfactor = 35, smoothplot = TRUE)$plot
@
    }
\end{subfigure}    
\begin{subfigure}[t]{\linewidth}
    \caption{Adjusted (Bullet 1-5 horizontally shifted) crosscuts at $x = 100$.\label{fig:smoothfac2}}{%
<<smoothfac2, echo=FALSE, fig.width=7, fig.height=2, out.width='\\textwidth'>>=
get_grooves(br111_bullet, smoothfactor = 5, smoothplot = TRUE)$plot
@
    }
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
    \caption{Adjusted (Bullet 1-5 horizontally shifted) crosscuts at $x = 100$.\label{fig:smoothfac3}}{%
<<smoothfac3, echo=FALSE, fig.width=7, fig.height=2, out.width='\\textwidth'>>=
get_grooves(br111_bullet, smoothfactor = 55, smoothplot = TRUE)$plot
@
    }
\end{subfigure}
\caption{\label{fig:varysmooth}Lines showing surface crosscuts at $x = 100$. A horizontal shift of the values of Bullet 1-5 to the right shows the similarity of the striation marks.}
\end{figure}
